Fuzzy Extractors for Noisy Sources with More Errors Than Entropy

### 2015-02-04 constantRate/ConstCompFuzzExt-crypto.tex
Minor fixes and lnotes

\title{Fuzzy Extractors From Noisy Sources With More Errors Than Entropy}
%\author{Ran Canetti \and Benjamin Fuller \and Omer Paneth \and Leonid Reyzin \and Adam Smith}
\blind{
\author{Ran Canetti\footnote{Email: {\tt canetti@cs.bu.edu}. Boston University and Tel Aviv University.} \and Benjamin Fuller\footnote{Email: {\tt bfuller@cs.bu.edu}.  Boston University and MIT Lincoln Laboratory.} \and Omer Paneth\footnote{Email: {\tt paneth@cs.bu.edu}. Boston University.} \and Leonid Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.  Boston University.} \and Adam Smith\footnote{Email: {\tt asmith@cse.psu.edu}.  Pennsylvania State University; work performed while at Boston University's Hariri Institute for Computing and RISCS Center, and Harvard University's
``Privacy Tools'' project.} }
}
\begin{document}
\maketitle

@@

Fuzzy extractors consist of a pair of algorithms: \gen (used once, at ``enrollment'') takes a source value $w$, and produces a key $r$ and a public helper value $p$.  The second algorithm \rep (used subsequently) takes this helper value $p$ and a close $w'$ to reproduce the original key $r$.
The correctness guarantee is that $r$ will be correctly reproduced by \rep as long as $w'$ is no farther than $t$ from $w$ in some metric space. In this work, we consider the Hamming metric.
 The security guarantee is that $r$ produced by \gen is close to uniform (information-theoretically \cite{DBLP:journals/siamcomp/DodisORS08} or computationally \cite{fuller2013computational}), even given $p$. This guarantee holds as long as $w$ comes from a high-quality distribution, which
traditionally has been defined as \emph{any} distribution with sufficient min-entropy $m$. Note that in this paper we consider only passive attacks on $p$; the problem of protecting against modification of $p$ has been addressed in, e.g., \cite{Boyen05secureremote,DKKRS12}, and, in particular, the random-oracle-based techniques of \cite{Boyen05secureremote} can be applied here, as well. \lnote{ok sentence?}

@@

In this work we restrict the distribution of the original reading $w$ and allow $w'$ to be an arbitrary point within distance $t$.  An alternative approach is to restrict the set of $w'$ where $\gen$ produces the correct key.%  A meaningful restriction of correctable errors is an open problem.

>>>>

\title{Fuzzy Extractors for Noisy Sources with More Errors Than Entropy}
%\author{Ran Canetti \and Benjamin Fuller \and Omer Paneth \and Leonid Reyzin \and Adam Smith}
\blind{
\author{Ran Canetti\footnote{Email: {\tt canetti@cs.bu.edu}. Boston University and Tel Aviv University.} \and Benjamin Fuller\footnote{Email: {\tt bfuller@cs.bu.edu}.  Boston University and MIT Lincoln Laboratory.} \and Omer Paneth\footnote{Email: {\tt paneth@cs.bu.edu}. Boston University.} \and Leonid Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.  Boston University.} \and Adam Smith\footnote{Email: {\tt asmith@cse.psu.edu}.  Pennsylvania State University; work performed while at Boston University's Hariri Institute for Computing and RISCS Center, and Harvard University's
``Privacy Tools'' project.} }
}
\begin{document}
\maketitle

@@

Fuzzy extractors consist of a pair of algorithms: \gen (used once, at ``enrollment'') takes a source value $w$, and produces a key $r$ and a public helper value $p$.  The second algorithm \rep (used subsequently) takes this helper value $p$ and a close $w'$ to reproduce the original key $r$.
The correctness guarantee is that $r$ will be correctly reproduced by \rep as long as $w'$ is no farther than $t$ from $w$ in some metric space. In this work, we consider the Hamming metric.
 The security guarantee is that $r$ produced by \gen is close to uniform (information-theoretically \cite{DBLP:journals/siamcomp/DodisORS08} or computationally \cite{fuller2013computational}), even given $p$. This guarantee holds as long as $w$ comes from a high-quality distribution, which
traditionally has been defined as \emph{any} distribution with sufficient min-entropy $m$. Note that in this paper we consider only passive attacks on $p$; the problem of protecting against modification of $p$ has been addressed in, e.g., \cite{Boyen05secureremote,DKKRS12}.  In particular, the random-oracle-based transform of \cite[Theorem 1]{Boyen05secureremote} can be applied to our constructions.

@@

In this work we restrict the distribution of the original reading $w$ and allow $w'$ to be an arbitrary point within distance $t$.  An alternative approach is to restrict the set of $w'$ where $\gen$ produces the correct key. \lnote{move this somewhere that makes more sense, probably above where we talk about a ball around a $w'$ and the obvious impossibility}%  A meaningful restriction of correctable errors is an open problem.
